Inter-Task Effects Induce Bias in Crowdsourcing

### 2014-10-12 docs/publications/2014.08_HCOMP/_man.tex
work on manuscript

%        File: pnas1.tex
%     Created: Wed Apr 30 04:00 pm 2014 E
% Last Change: Wed Apr 30 04:00 pm 2014 E
%
\documentclass[letterpaper,twocolumn]{article}
\usepackage[hmargin=0.75cm,vmargin=0.75cm]{geometry}
\usepackage{scrextend}
\usepackage{graphicx}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}
\usepackage{algorithm2e}
\usepackage{amsthm}

@@

\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}

\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\setlength{\parindent}{0cm}
\setlength{\parskip}{4mm plus1mm minus1mm}

\title{Inter-task effects induce bias in crowdsourcing}
\author{Edward Newell, Derek Ruths}

\parindent0pt \parskip8pt

\begin{document}
\maketitle
\section*{Abstract}
Microtask platforms like Amazon Mechanical Turk provide a cheap and fast means
to engage participants for scientific reasearch.  
Workers on such platforms prefer to work on batches of tasks of the same 
type, so we investigate the potential for the content of earlier tasks 
to influence worker performance in later tasks, which we call ``inter-task'' 
effects.  
Existing research investigates the impact of various design factors, such as 
``framing'', on the quality of crowdsourced content, but does not, to 
our knowledge, address inter-task effects.  
We employ a canonical image-labeling task on the Amazon Mechanical Turk 
platform, to measure both inter-task and framing effects, in terms of their 
impact to the content and specificity of the labels workers provide.
We also introduce an algorithmic definition of priming, which measures the 
worst-case bias that priming effects introduce into crowdsourced content.
We find that inter-task effects produce a much stronger impact than framing, 
and find that our algorithmic definition yields a powerful, generalized measure
for priming effects when combined with machine learning algorithms.

\section*{Introduction}

Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun, a sense of purpose, and remuneration 
\cite{kazai2013analysis, Antin20122925}.  
Originally used to distribute clerical work, these platforms 
increasingly serve as a fast and cheap means to engage experimental 
participants and manually annotate datasets in a research 
setting \cite{snow2008cheap}.  
Tasks involving qualitative
judgment (e.g. flagging inappropriate images), natural language annotation,
and object recognition are commonplace, since it is difficult to achieve 
comparable performance using only computers \cite{yuen2011survey}.
%Generally the worker is first given some orientation to the task, and then 
%performs the task repeatedly (e.g. label several images, one after 
%the other).

Such platforms make human cognition a fluid resource: it is available 
on demand in small units, with low transaction 
cost, from anywhere via the 
Internet\footnote{\href{http://mturk.com}{http://mturk.com}}.
The task requester can 
interact with the platform like a compute server, seamlessly 
integrating human and machine computation.  Researchers have put forward the 
term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
term: the original meaning of `computer' was a person who performs 
computations, its reference to machines being a personification brought into 
usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
microtask platforms as a new computing architecture
\cite{5543192}.

Here, we highlight an important way in which HPUs differ from CPUs, with 
serious implications for the design of tasks.  It is well known that people 
are subject to priming effects 
\cite{BJOP:BJOP1796, No2007, beller1971priming} and, in particular, task-repetition effects
\cite{Gass1999549, sohn2001task}.  
We investigate the effect that previously completed tasks have on workers'
responses during subsequent ones. We call such effects 
\textit{inter-task priming}.  Inter-task priming would amount to a kind of
\textit{hysteresis}, meaning that HPU output is not only a function of the 
current input, but also of the history of inputs.

There has been considerable investigation into the factors that affect HPU 
output on crowdsourced microtask platforms.  Studies have shown that 
there is a great deal of variance in worker attention and 
accuracy \cite{kazai2013analysis}.  Factors that affect the quality of HPU 
output include level of pay\cite{kazai2013analysis}, 
training\cite{le2010ensuring}, screening workers\cite{paolacci2010running}, 
and user-interface design
\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
by testing the effects of disclosing the role of a task within the 
context of a study \cite{Kinnaird2012281}, and disclosing the ultimate 
purpose of that study \cite{chandler2013breaking}.  However, to our knowledge, 
no study has investigated the effects of inter-task priming.

To characterize the effects of inter-task priming, we present a novel  
\textit{algorithmic definition of priming}, along with a general method 
for measuring priming effects using machine learning algorithms.  
Existing work on priming effects focuses on the internal psychological 
mechanisms of priming, but here we are interested in how the treatment of 
workers can impact an application of human computation. This leads us to 
quantify priming in terms of the algorithmic distinguishability of priming
treatments.

In the present work, we investigate inter-task priming using image-labeling 
tasks on the AMT platform.  
Each worker is required to label ten images 
featuring 
food and culture.  We regard these images as being made up of an 
\textit{initial} and \textit{final set}, but, crucially, there is no
distinction made between these sets, nor any interruption in the flow of tasks 
from the view of the worker.
Each worker is randomly assigned one of three initial sets, but the final set
of images is always the same.  We analyze the effect that the assignment of 
initial set has on workers' attribution of labels to the final set.  We 
measure effects using our novel approach, as well as looking for changes in 
the content of labels and label specificity based on an ontology we 
developed for that purpose.

As a point of comparison, we subject some groups of workers to a kind of
\textit{framing}: we disclose a fictitious, semantically-loaded name for 
requester funding the tasks.
The names were chosen to suggest the requester's interest in 
a specific aspect of the image content.  One might reasonably expect that this 
would orient workers to provide a greater quantity and specificity of labels 
which relate to this ``preferred'' content.

Surprisingly, we find that inter-task effects on label orientation and 
specificity are much stronger than those brought about by framing tasks with a 
funder name.  Our results show that initial tasks can introduce significant 
bias in subsequent worker labeling.  Interestingly, we find that inter-task
effects can be used to induce greater specificity.  Our results suggest that
workers attribute more specific labels when labeling a series of images that
that are more similar to one another.  This suggests that careful 
consideration should be given to the bundling of tasks when designing a study 
using a microtask platform.

Our analysis also highlights important advantages of our novel definition of 
priming.  Our approach relies on no prior knowledge about the nature
of the task task whatsoever.  In contrast, we also sought to detect priming
based on its direct effects on label content and specificity, implicitly
drawing on prior knowledge about the images and label semantics.
Remarkably, while being more general, our novel approach was also more 
sensitive.  This suggests that our measurement approach could be applied in 
cases where one does not \emph{a priori} know whether any priming has occurred, 
nor what the effects might be.

\subsection*{An algorithmic definition of priming}

In psychology, the effects of priming are usually measured in terms of a 
change in the  
speed or accuracy of responses in a task, or in the ability to recognize a 
stimulus object (e.g. a spoken word or an image) when the object is noisier, 
fainter, or briefer.  Methods are also employed to measure processes
in the brain of the participant, such as by fMRI.  These approaches are 
well-suited to studying the underlying psychological mechanisms at work.

Our purpose is different: we are interested in assessing the ramifications
that priming of HPUs could have on the applications to which they are employed.
This influences the approach we take to measurement in two ways.  First, we 
switch from focusing on the internal mechanisms of HPUs to focusing strictly 
on the HPU outputs.  Second, we cannot \textit{a priori} know the 
application for which HPUs are being employed, but we would like to measure 
any effects that could in principle impact the application.  These 
considerations motivate us to define priming effects in terms of the 
algorithmic distinguishability of primed output.

One difficulty in constructing a definition of priming is that there would 
appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  A 
participant 
always approaches a task in \textit{some} state of mind.  If no priming 
condition is applied, then the participant is simply primed by her
exposures prior to the experiment, which cannot be known by the experimenter.  
While arguments can surely be made that one treatment or another is 
\textit{more} 
``neutral'', we refrain from proposing a canonical ``null priming treatment''. 
Instead, we define priming relatively, and speak of one treatment being 
\textit{differently primed} from another.

A definition of priming must also consider that the effects of priming will
manifest differently depending on the task that participants perform 
subsequent to priming:  two priming treatments that
produce markedly different output for one task might be 
indistinguishable under another task.  Thus, we define priming
with respect to a task.

A final factor to consider is that people will always differ in their initial
knowledge, specific aptitudes, and in many other intrinsic aspects.  Moreover,
priming may not be ``complete'', in the sense that people's experiences before
priming may continue to have residual effects.  Therefore, we define priming 
in relation to populations, which we regard as having stable distributions of
such latent attributes.

To set up the definition, when a population of people $\mathcal{J}$ performs
a task $\mathcal{T}$ thus producing a population of task-outputs $\mathcal{L}$,
we will write $\mathcal{T}(\mathcal{J}) = \mathcal{L}$.

\vspace{2mm}
\begin{mydef}
	\upshape
	Two mutually exclusive populations of people, $\mathcal{P}_0$ and 
	$\mathcal{P}_1$, are uniformly and randomly subsampled from an initial 
	population $\mathcal{P}$, are exposed to (possibly) different priming 
	treatments, and then perform a task $\mathcal{T}$, 
	producing task-outputs $\mathcal{T}(\mathcal{P}_0)$ and 
	$\mathcal{T}(\mathcal{P}_1)$.
	These populations are subsampled, producing 
	$P_0 \subset \mathcal{P}_0$ and
	$P_1 \subset \mathcal{P}_1$. A uniform, random bit is chosen, 
	$b\in _R \{0,1\}$, and a single worker $p$ is uniformly and randomly 
	sampled from 
	$\mathcal{P}_b \setminus P_b$.
	We say that $\mathcal{P}_0$ and $\mathcal{P}_1$ 
	\emph{differ in priming by a degree at least $\theta$},
	if there exists a \emph{distinguisher algorithm} $\mathcal{A}$ that takes as input 
	$\langle\mathcal{T}(J)$, $\mathcal{T}(K)$, $\mathcal{T}(\{p\})\rangle$
	and outputs a guess for $b$ with accuracy $\frac{1+\theta}{2}$.  
\end{mydef}

In the language of computer science, $\mathcal{A}$ is a classifier performing
a binary classification.  The measure $\theta$ can range between 0 and 1, and 
indicates how much better the performance of the best possible classifier is 
compared to a random guess. We intentionally leave the details of 
$\mathcal{A}$ unrestricted because $\theta$ should depend on the potential 
for two populations to be distinguished, based on their inherent differences, 
rather than on the performance of a particular classifier.

In practice, some particular classifier $\mathcal{C}$ must be used and a 
statistical estimate of its performance $\hat{\theta}_\mathcal{C}$ obtained. 
$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
theoretical value $\theta$ from the definition, because there might 
exist some other classifier $\mathcal{C}'$ with 
$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
Here, we use a Naive Bayes classifier because it simple and performs well 
across a broad range of classification tasks.

To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice is to be
made between two options on the basis of worker outputs (e.g. whether or not 
to flag an image as inappropriate). Any such binary choice has a formal 
structure of a trained classifier (i.e. a distinguisher which discards the 
first two inputs). This means that $\hat{\theta}_\mathcal{C}$ estimates a 
lower bound for the worst-case bias introduced in such a binary decision when 
one failed to control for priming effects.

\subsection*{Experimental Setup}

\begin{figure*}
	\centering{
	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
	\caption{ \footnotesize{
		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
		various treatments.  The difference in priming between each pair of 
		treatments 
		was determined by cross-validation of a Naive Bayes classifier trained
		to classify workers based on the labels they attributed to the first
		image of the final image set. Each panel compares a basis treatment,
		indicated above the panel, to various treatments indicated on the
		abscissa.  We can conclude, with 95\% confidence, that the classifier
		is performing better than chance when $\hat{\theta}_\text{NB}$ 
		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
		the calculation of this confidence threshold.
	}}
}
\end{figure*}

\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder & Priming Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

	\caption{ \footnotesize{ 
		Workers were uniformly randomly assigned to one of the 
		treatments listed above. 
		The full funder names used were 
		``The Global Foundation for Cultural Recognition'' and 
		``The National Foundation for Nutritional Awareness''.  
		The ambiguous, cultural, and ingredients initial image sets are shown 
		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
	}}
	\label{table:1}
\end{table}

We solicited 900 AMT workers to perform an image-labeling task relating to
food and culture.  The workers were randomly assigned to one of seven 
treatments shown in \textbf{Table 1}.  Workers were first shown brief 
instructions.  Depending on their treatment, workers were then shown the 
name of a research funder, or this step was skipped.  When shown, 
the funder name was either
``The Global Foundation for Cultural Recognition'', or 
``The National Foundation for Nutritional Awareness''.

Next, workers were
shown ten images, one at a time. Workers were required to label each image 
with five descriptive labels before moving on to the next.  For the purpose 
of analysis, we divide the images
into \textit{initial} and \textit{final} sets, comprising respectively the 
first five and last five images shown.  As mentioned, from the perspective of 
the worker, there was no 
distinction or interruption between the initial and final sets. 
Depending on the treatment to which the worker was assigned, one of three 
initial image sets was chosen. The final image set was the same for all 
treatments.

For the final image set, we chose 
images that contained prepared meals and featured a prominent, identifiable 
culture (see \textbf{Fig. 4}).  We intended that the content of these images 
would elicit labels focusing on food or culture (or both).
We refer to the three initial image sets as the ``ambiguous'', ``cultural'', 
and ``ingredients'' sets.  The ambiguous set was chosen to
be very similar to the final image set, in the sense that it consisted of
images of prepared meals (see \textbf{Fig. 5}).  However, its cultural 
features were intended to be less prominent.  The cultural set featured 
iconic cultural scenes, but no food at all (see \textbf{Fig. 6}).  Finally, 
images from the 
ingredients set depicted separated ingredients, but, 
like the ambiguous set, were chosen to avoid prominent cultural features (see 
\textbf{Fig. 7}).  See the \textbf{Materials and Methods} section for further 
details.

\subsection*{Results}
\paragraph{Inter-task priming was strong, while framing was weak.}
We tested for priming effects using our algorithmic definition, implemented 
with a Naive Bayes classifier.  This involved measuring the classifier's 
accuracy in classifying workers chosen from a pair of treatments during 
cross-validation (see \textbf{Methods} for details).  The classifier's accuracy
for cross-validations involving each pair of treatments is shown in 
\textbf{Fig.1}.

With some exceptions, the classifier performed significantly better 
than chance when distinguishing treatments that had different initial image 
sets.  This demonstrates that inter-task effects were strong for the labeling 
tasks.  Of the sixteen treatment pairs having different initial images, there 
were three cases where the classifier performance was on par with chance. 
Each of these cases involved distinguishing workers shown the ambiguous set 
from ones shown the ingredients set.  The reason for the low 
distinguishability of workers from these treatments might be because
the ambiguous and ingredients sets are somewhat similar to one another.
We will come back to this point later when we discuss the degree of similarity 
between image sets.

In contrast, the classifier never performed significantly better than chance
when distinguishing treatments that differed only in the funder name shown. 
Thus, framing effects were rather weak.

\paragraph{Earlier tasks influenced workers' level of specificity.} 
\begin{figure*}
	\centering{
		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
	\caption{\footnotesize{
		\textbf{A}) Percent label composition (culture- vs food-oriented 
		labels) for 
		various images and treatments.  
		\textbf{B}) Relative specificities of treatments
		indicated along the abscissa compared to those indicated above the 
		plot.  The size of the bar indicates how much more specific
		the labels from one treatment are compared to the other, and points 
		toward in the direction of the more specific treatment.
	}}
}
\end{figure*}

\paragraph{Earlier tasks orient workers' focus during later tasks.} 
We next investigated the \textit{nature} of the inter-task effects.  Since the
initial images were chosen to emphasize either food (ingredients set) or 
culture (cultural set), we looked for effects in the number of culture- and 
food-oriented labels that workers attributed to the final image set.

To this end, we constructed an ontology from the labels attributed to the 
test images.  The ontology was constructed as a directed acyclic graph, with 
edges pointing from more general labels to more specific ones.
For example, our ontology contains the path \texttt{food} $\to$ 
\texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}. We 
provide more detail about the construction of the ontology in the 
\textbf{Materials and Methods} section.

>>>>

%        File: pnas1.tex
%     Created: Wed Apr 30 04:00 pm 2014 E
% Last Change: Wed Apr 30 04:00 pm 2014 E
%
\documentclass[letterpaper]{article} 
\usepackage{aaai} 
\usepackage{times} 
\usepackage{helvet} 
\usepackage{courier} 
\setlength{\pdfpagewidth}{8.5in} 
\setlength{\pdfpageheight}{11in} 
%%%%%%%%%%
% PDFINFO for PDFLATEX
% Uncomment and complete the following for metadata (your paper must compile with PDFLATEX)
\pdfinfo{
	/Title Inter-Task Effects Induce Bias in Crowdsourcing
	/Author Edward Newell
	/Keywords priming, framing, crowdsourcing
}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}
\usepackage{algorithm2e}
\usepackage{amsthm}
\usepackage{caption}

@@

%\setlength{\parindent}{0cm}
%\setlength{\parskip}{4mm plus1mm minus1mm}

%%%%%%%%%%
% Section Numbers
% Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
% \setcounter{secnumdepth}{0} %%%%%%%%%%
\title{Inter-Task Effects Induce Bias in Crowdsourcing}
\author{Edward Newell\footnote{bla} \and Derek Ruths\\
School of Computer Science, McGill University, Montreal, Canada\\
$^*$\texttt{edward.newell@mail.mcgill.ca}\\
}
%%%%%%%%%%
% Body of Paper Begins
\begin{document}
\maketitle
\section*{Abstract}
Microtask platforms allow researchers to engage participants quickly and 
inexpensively.
Workers on such platforms probably perform many tasks in succession,
so we investigate interactions between earlier tasks and later ones, which we 
call ``inter-task'' effects.  
Existing research investigates many task design factors, such as 
``framing'', on the quality of responses, but to our knowledge, does not 
address inter-task effects.  
We use a canonical image-labeling task on Amazon Mechanical Turk 
to measure the impact of inter-task and framing effects on the focus and 
specificity of labels that workers provide.
We also introduce an algorithmic definition of priming, which measures the 
worst-case bias introduced into responses.
We find that inter-task effects produced a much stronger impact than framing, 
and demonstrate that our novel priming definition yields a generalized 
measure of priming effects when combined with machine learning algorithms.
\paragraph{Keywords:} priming, framing, crowdsourcing.
\section*{Introduction}
Microtask crowdsourcing platforms like Amazon Mechanical Turk (MTurk) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun, a sense of purpose, and remuneration 
\cite{kazai2013analysis,Antin20122925}.  
Originally used to distribute clerical work, these platforms 
increasingly serve as a fast and cheap means to engage experimental 
participants in a research 
setting \cite{snow2008cheap}.

The task requester can interact with the platform like a compute server, 
seamlessly 
integrating human and machine computation.  Researchers have put forward the 
term HPU (Human co-Processing Unit), viewing the introduction of 
microtask platforms as a new computing architecture
\cite{5543192}.

Here, we highlight an important way in which HPUs differ from CPUs, with 
serious implications for the design of tasks.  It is well known that people 
are subject to priming effects 
\cite{BJOP1796,No2007,beller1971priming} and, in particular, task-repetition effects
\cite{Gass1999549,sohn2001task}.  
We investigate the effect that previously completed tasks have on workers'
responses during subsequent ones. We call such effects 
\textit{inter-task priming}.  Inter-task priming would amount to a kind of
\textit{hysteresis}, meaning that HPU output is not only a function of the 
current input, but also of the history of inputs.

There has been considerable investigation into the factors that affect the 
quality and quantity of micro-task completion.  These include the level of 
pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, screening of 
workers \cite{paolacci2010running}, and user-interface design 
\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
by testing the effects of disclosing the workflow context 
\cite{Kinnaird2012281}, and the purpose of tasks 
\cite{chandler2013breaking}.  To our knowledge, no study has investigated the 
effects of inter-task priming.

To characterize the effects of inter-task priming, we present a novel  
\textit{algorithmic definition of priming}, and a general method 
for measuring priming effects using machine learning algorithms.  
Rather than focus on internal psychological mechanisms, our definition 
focuses on the impact that priming has to the downstream application of human 
computation, providing a generalized measure of bias.

In the present work, we investigate inter-task priming on the Amazon 
Mechanical Turk platform, using an image-labeling task, one of the most common 
kinds of tasks on that platform 
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  The task requires workers to label ten 
images featuring 
food and culture.  We regard these images as being made up of an 
\textit{initial} and \textit{test set}, but, crucially, there is no
distinction made between these sets, nor any interruption in the flow of tasks 
from the view of the worker.
We vary the initial set of images, while keeping the test set the same to 
analyze the effect that that the initial images have on the labels that 
workers' attribute to the test set.  We measure effects using our novel 
approach, as well as looking for changes in the content of labels and label 
specificity based on an ontology we developed for that purpose.

As a point of comparison, we subject some groups of workers to a kind of
\textit{framing}: we disclose a fictitious, semantically-loaded name for 
the requester funding the tasks.
The names were chosen to suggest the requester's interest in a specific 
aspect of the image content.  We expect this would cause workers 
to provide more labels, and greater specificity, relating to this 
``preferred'' content.

Surprisingly, we find that inter-task effects are much stronger than the 
framing.  Our results show that initial tasks can significantly alter the 
focus of worker's labels.  Interestingly, we find that inter-task
effects can be used to induce greater specificity.  Our results suggest that
workers attribute more specific labels when labeling a series of images that
that are more similar to one another.  This suggests that careful 
consideration should be given to the bundling of tasks when designing a study 
using a microtask platform.

Our analysis also highlights important advantages of our novel definition of 
priming.  Our approach incorporates no prior knowledge about the nature
of the task whatsoever.  In contrast, we also sought to detect priming
based on its direct effects on label content and specificity,
drawing on prior knowledge about the images and label semantics.
Remarkably, while being more general, our definition yields a more sensitive
measure of priming when combined with machine learning algorithms. 
This approach could be applied to detect priming when one does not 
\emph{a priori} know whether any priming has occurred, 
nor what the nature of the effects might be.
\subsection*{An algorithmic definition of priming}
Our goal in creating a definition of priming is to capture the effects of 
priming on human computation \textit{applications}.  This motivates us to 
seek a definition of priming in terms of its ability alter HPU 
output rather than in terms of psychological mechanisms.

We define priming with respect to a task $\mathcal{T}$.  People will always differ in their initial knowledge, specific 
aptitudes, and in many other intrinsic aspects.  Moreover, priming may not be 
``complete'', in the sense that people's experiences before
priming may continue to have residual effects.  Therefore, we define priming 
in relation to populations, which we regard as having stable distributions of
such latent attributes.

One difficulty in constructing a definition of priming is that there would 
appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  
While arguments could perhaps be made that one treatment or another is 
\textit{more} ``neutral'', we choose to define priming relatively, and speak 
of one treatment being \textit{differently primed} from another.

To set up the definition, when a population of people $\mathcal{P}$ performs
a task $\mathcal{T}$ thus producing outputs $\mathcal{L}$,
we will write $\mathcal{T}(\mathcal{P}) = \mathcal{L}$.

\vspace{2mm}
\begin{mydef}
	\upshape
	Two mutually exclusive populations of people, $\mathcal{P}_0$ and 
	$\mathcal{P}_1$, are uniformly and randomly subsampled from an initial 
	population $\mathcal{P}$, and are exposed to (possibly) different priming 
	treatments. Each population performs a task $\mathcal{T}$, 
	producing outputs $\mathcal{T}(\mathcal{P}_0)$ and 
	$\mathcal{T}(\mathcal{P}_1)$.
	These populations are subsampled, producing 
	$P_0 \subset \mathcal{P}_0$ and
	$P_1 \subset \mathcal{P}_1$. A uniform, random bit is chosen, 
	$b\in _R \{0,1\}$, and a single worker $p$ is uniformly and randomly 
	sampled from 
	$\mathcal{P}_b \setminus P_b$.
	We say that $\mathcal{P}_0$ and $\mathcal{P}_1$ 
	\emph{differ in priming by a degree at least $\theta$},
	if there exists a \emph{distinguisher algorithm} $\mathcal{A}$ that takes as input 
	$\langle\mathcal{T}(J)$, $\mathcal{T}(K)$, $\mathcal{T}(\{p\})\rangle$
	and outputs a guess for $b$ with accuracy $\frac{1+\theta}{2}$.  
\end{mydef}

\begin{figure*}
	\centering{
	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
	\caption{ \footnotesize{
		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
		various treatments.  The difference in priming between each pair of 
		treatments 
		was determined by cross-validation of a Naive Bayes classifier trained
		to classify workers based on the labels they attributed to the first
		image of the test set. Each panel compares a basis treatment,
		indicated above the panel, to various treatments indicated on the
		abscissa.  We can conclude, with 95\% confidence, that the classifier
		is performing better than chance when $\hat{\theta}_\text{NB}$ 
		exceeds 0.168, indicated by the dotted line.
	}}
}
\end{figure*}

In the language of computer science, $\mathcal{A}$ is a classifier performing
a binary classification.  The measure $\theta$ can range between 0 and 1, and 
indicates how much better the performance of the best possible classifier is 
compared to a random guess. We intentionally leave the details of 
$\mathcal{A}$ unrestricted because the theoretical value of $\theta$ should 
depend on the inherent differences between the populations, rather than on 
the performance of a particular classifier.

In practice, some particular classifier $\mathcal{C}$ is tested (using e.g. 
cross-validation) yielding a statistical estimate of its performance 
$\hat{\theta}_\mathcal{C}$. This
$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
theoretical value of $\theta$, because there might 
exist some other classifier $\mathcal{C}'$ with 
$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
For our experiment, we use a Naive Bayes classifier because it is easy to
implement and performs well across a broad range of classification tasks.

To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice 
$\mathcal{C}$ is to be made between two options on the basis of worker 
outputs (e.g. whether or not to flag an image as inappropriate). Any such 
binary choice has the formal structure of a distinguisher that only considers 
the last of its three inputs. Thus, we can directly compare $\mathcal{C}$ to 
the optimal distinguisher, $\mathcal{A}$.  If, prior to knowing the input to 
$\mathcal{C}$, either of its outcomes is equally likely, then the worst 
possible bias that priming can introduce is bounded above by $\theta$. 
This means that $\hat{\theta}_\mathcal{C}$ estimates a 
lower bound for the worst-case bias introduced in a binary 
decision that provides a full bit of information, made on the basis of worker 
outputs, when one failed to control for the corresponding priming treatments.
\subsection*{Experimental Setup}
\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder & Priming Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

	\caption{ \footnotesize{ 
		Workers were uniformly randomly assigned to one of the 
		treatments listed above. 
		The full funder names used were 
		``The Global Foundation for Cultural Recognition'' and 
		``The National Foundation for Nutritional Awareness''.  
		The ambiguous, cultural, and ingredients initial image sets are shown 
		in \textbf{Figs. S2}, \textbf{S3}, and \textbf{S4}.
	}}
	\label{table:1}
\end{table}
We solicited 900 MTurk workers to perform an image-labeling task relating to
food and culture.  The workers were randomly assigned to one of seven 
treatments shown in \textbf{Table 1}.  Depending on their treatment, workers were then shown the 
name of a research funder, or this step was skipped.
Next, workers were shown ten images, one at a time and were required to provide
five labels for each.  For the purpose of analysis, we divide the images
into \textit{initial} and \textit{test} sets, comprising respectively the 
first five and last five images.  From the perspective of the worker, there 
was no distinction or interruption between the initial and test sets. 
Depending on the treatment, one of three initial image sets was chosen, but
the test set was always the same.

The test image set comprised images containing prepared meals and featured a 
prominent, identifiable culture (see \textbf{Fig. S1}).
To identify the initial image sets, we use the names ``ambiguous'', 
``cultural'', and ``ingredients''.  The ambiguous set was chosen to
be similar to the test set, in the sense that it consisted of
images of prepared meals (see \textbf{Fig. S2}),  but its cultural 
features were less prominent.  The cultural set featured 
iconic cultural scenes, but no food at all (see \textbf{Fig. S3}).  Images from 
the ingredients set depicted separated ingredients, but, 
like the ambiguous set, avoided prominent cultural features (see 
\textbf{Fig. S4}).
\subsection*{Results}
\paragraph{Inter-task priming was strong, while framing was weak.}
We tested for priming effects using our algorithmic definition, implemented 
with a Naive Bayes classifier.  The classifier's accuracy
in cross-validations involving each pair of treatments is shown in 
\textbf{Fig.1}.

With some exceptions, the classifier performed significantly better 
than chance when distinguishing treatments that had different initial tasks.  
This demonstrates that inter-task effects were strong. Of the sixteen 
treatment pairs having different initial tasks, the classifier was unable to
distinguish treatments significantly better than chance in three cases.
Each cases involved distinguishing treatments having the ambiguous and 
ingredients set.  Later we discuss the similarity between image sets, and 
we will argue that this is because the ambiguous and ingredients sets are 
similar.

\begin{figure*}
	\centering{
		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
	\caption{\footnotesize{
		\textbf{A}) Percent label composition (culture- vs food-oriented 
		labels) for 
		various images and treatments.  
		\textbf{B}) Relative specificities of treatments
		indicated along the abscissa compared to those indicated above the 
		plot.  The size of the bar indicates how much more specific
		the labels from one treatment are compared to the other, and points 
		toward in the direction of the more specific treatment.  Error bars
		indicate 95\% confidence intervals.
	}}
}
\end{figure*}
In contrast, the classifier never performed significantly better than chance
when distinguishing treatments that differed only in framing.  Thus, framing 
effects were rather weak.  In fact, framing effects were generally weak in
our results, so we omit treatments involving framing from the remainder of
our presentation to save space.  We encourage the interested reader to look
at the results for these treatments in the supplementary material.
\paragraph{Earlier tasks orient workers' focus during later tasks.} 
Since the initial images were chosen to emphasize either food (ingredients set)
or culture (cultural set), we looked for effects on the number of culture- and 
food-oriented labels that workers attributed to the test image set.

To this end, we constructed an ontology from the labels attributed to the 
test images.  In the ontology, edges point from more general labels to more 
specific ones.  For example, the ontology contains the path \texttt{food} 
$\to$ \texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}.

Since food is a central feature 
of culture, our ontology contains many labels that have both \texttt{food}
and \texttt{culture} in their ancestry.  Nevertheless, there were many 
food-oriented labels, such as \texttt{bread}, which lacked specific cultural 
connections, as well as non-food, culture-oriented labels, such as 
\texttt{russian dolls}.

\begin{figure}
	\centering{
	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
	\caption{\footnotesize{
		\textbf{A}) Difference in priming between \textsc{ambg} and 
		$\textsc{cult}_{img}$ measured based on the accuracy of a Naive Bayes 
		classifier during cross-validation, when trained on labels from the
		test images indicated along the abscissa.
		\textbf{B}) Excess cultural orientation of labels attributed to
		the test images indicated on the abscissa, by workers from
		$\textsc{cult}_{img}$ relative to those attributed by workers from
		\textsc{ambg}, calculated using \textbf{Eq. 3}.  Error bars indicate
		95\% confidence intervals.
	}}
}
\end{figure}
When we tallied labels attributed to the first image of the test set, 
we found that workers from $\textsc{cult}_{img}$ produced significantly 
more culture-oriented labels and less food-oriented ones than those from
\textsc{ambg}
(see \textbf{Fig. 2A}).  The inter-task effect was so strong that the 
proportion of food- and culture-oriented labels in $\textsc{cult}_{img}$ was
essentially the reverse of that in \textsc{ambg}.  However, the 
composition of labels attributed by $\textsc{ingr}_{img}$
was not significantly different from those attributed by \textsc{ambg}.  This 
shows that inter-task effects \textit{can} profoundly alter workers' focus. 
Again, we 
will argue later that the ambiguous and ingredients image sets are, in fact, 
quite similar.
\paragraph{Earlier tasks influenced workers' level of specificity.} 
Using the ontology described in the previous section, we can compare the 
specificity of two labels $\ell_1$ and $\ell_2$. We say that $\ell_2$ is more 
specific than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to 
$\ell_2$.  If there is no directed path between labels, we say they are  
\textit{non-comparable}.  For example, \texttt{tomato} was more specific than 
\texttt{food}, while \texttt{statue} and \texttt{food} were non-comparable.

We can then define the relative specificity of two workers with respect to 
test-image $i$ as $s_i(u,v)$:
